Week 1 test
========================================================

Question 1: 
--------------------------------------------------------

The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here: 

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv 

and load the data into R. The code book, describing the variable names is here: 

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FPUMSDataDict06.pdf 

How many properties are worth $1,000,000 or more?


First check existence of data directory, create if not, then check existence of file, download if not, and load into a variable 

Didnt put a timestamp because this is a one shot code

```{r}
if(!file.exists("dataTest")){
dir.create("dataTest")
}

dataOrigin<-"https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv" 

destfile<-"./dataTest/dataQ1.csv"

if(!file.exists(destfile)){
    getwd()
    download.file(dataOrigin,destfile,method="curl")
}

dataQ1<-read.csv(destfile)
head(dataQ1)
```

La columna que tiene el valor que nos interesa segun el codebook se llama VAL, nos quedamos solo con esa 

```{r}
dataQ1<-subset(dataQ1,select="VAL")
head(dataQ1)
```

Los valores estan codificados en clave,  las posesiones con mayor valor que 1M$ tienen el codigo 24

```{r}
sum(dataQ1$VAL==24,na.rm=TRUE)
```

Y la respuesta es 53  Lo que esta bastante bien por que es una de las posibilidades


Question 2: 
--------------------------------------------------------
Use the data you loaded from Question 1. Consider the variable FES in the code book. Which of the "tidy data" principles does this variable violate?
Numeric values in tidy data can not represent categories.
Tidy data has one variable per column.
Tidy data has variable values that are internally consistent.
Each tidy data table contains information about only one type of observation

Veamos que dice el codebook de la variable FES 

"FES 1 
 Family type and employment status "

Con lo que tenemos dos variables por columna y la respuesta es la que en esta version del examen sale la segunda 


Question 3: 
--------------------------------------------------------

Download the Excel spreadsheet on Natural Gas Aquisition Program here: 

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx 

Read rows 18-23 and columns 7-15 into R and assign the result to a variable called:
 dat 
What is the value of:
 sum(dat$Zip*dat$Ext,na.rm=T) 
(original data source: http://catalog.data.gov/dataset/natural-gas-acquisition-program) 

Empezamos buscando la existencia del archivo y directorio  y si no lo hay lo creamos y descargamos


```{r}
if(!file.exists("dataTest")){
dir.create("dataTest")
}

dataOrigin<-"https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx" 

destfile<-"./dataTest/dataQ3.xlsx"

if(!file.exists(destfile)){
    getwd()
    download.file(dataOrigin,destfile,method="curl")
}


``` 


Ahora que ya tenemos el archivo podemos cargarlo a la variable dat como piden (es necesario haber instalado con install.packages el paquete "xlsx")


```{r}
library(xlsx)
dat<-read.xlsx(destfile,sheetIndex=1,header=TRUE,rowIndex=18:23,colIndex=7:15)
head(dat)
```

y ya metemos la cuentecita del examen, que no sirve para nada mas que para el examen todo sea dicho 

```{r}
sum(dat$Zip*dat$Ext,na.rm=T) 
```



Question 4
-------------------------------------------------
Read the XML data on Baltimore restaurants from here: 

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml 

How many restaurants have zipcode 21231?


Empezamos buscando la existencia del archivo y directorio  y si no lo hay lo creamos y descargamos


```{r}
if(!file.exists("dataTest")){
dir.create("dataTest")
}

dataOrigin<-"https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml" 

destfile<-"./dataTest/dataQ4.xml"

if(!file.exists(destfile)){
    getwd()
    download.file(dataOrigin,destfile,method="curl")
}

``` 


Vamos a cargar el archivo
```{r}
library(XML)
document<-xmlTreeParse(destfile,useInternalNodes=T)

rootNode<-xmlRoot(document)
```

Hay una forma bastante facil de hacerlos sabiendo que el tag que buscamos se llama zipcode,  extraemos todos los valores de zipcode a un archivo

```{r}
zips<-xpathSApply(rootNode,"//zipcode",xmlValue)
```

Y sumamos los que coinciden con el 21231 

```{r}
sum(zips == "21231")
```


Question 5
-------------------------------

Aunque es evidente aqui pondre el codigo para comprobarlo y tener guardados los tiempos 

Va a haber que usar system.time
