Test2Q2ss
========================================================

Question 2
The sqldf package allows for execution of SQL commands on R data frames. We will use the sqldf package to practice the queries we might send with the dbSendQuery command in RMySQL. Download the American Community Survey data and load it into an R object called
 acs


https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv 

Which of the following commands will select only the data for the probability weights pwgtp1 with ages less than 50?
sqldf("select * from acs where AGEP < 50")
sqldf("select pwgtp1 from acs where AGEP < 50")
sqldf("select * from acs")
sqldf("select pwgtp1 from acs")


```{r}
if(!file.exists("dataTest")){
dir.create("dataTest")
}

dataOrigin<-"https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv" 

destfile<-"./dataTest/dataQ2.csv"

if(!file.exists(destfile)){
    getwd()
    download.file(dataOrigin,destfile,method="curl")
}

acs<-read.csv(destfile)
head(acs)
```

Carguemos el package y vemos que sacan las distintas propuestas 

```{r}
library(sqldf)

head(sqldf("select * from acs where AGEP < 50"))
head(sqldf("select pwgtp1 from acs where AGEP < 50"))
head(sqldf("select * from acs"))
head(sqldf("select pwgtp1 from acs"))
```

En este caso es claro que es la respuesta que solo saca una columna, y desde luego la cuarta no puede ser  (he puesto unos heads por que si no es infumable)

### Question 3

Using the same data frame you created in the previous problem, what is the equivalent function to unique(acs$AGEP)
sqldf("select unique AGEP from acs")
sqldf("select distinct AGEP from acs")
sqldf("select distinct pwgtp1 from acs")
sqldf("select unique * from acs")


y simplemente corremos las 5 posibilidades
```{r}
unique(acs$AGEP)
sqldf("select unique AGEP from acs")
sqldf("select distinct AGEP from acs")
sqldf("select distinct pwgtp1 from acs")
sqldf("select unique * from acs")
```

Y aqui comparamos y quitamos los que tienen error