Week 3 Quiz
========================================================

Question 1

The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here: 

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv 

and load the data into R. The code book, describing the variable names is here: 

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FPUMSDataDict06.pdf 

Create a logical vector that identifies the households on greater than 10 acres who sold more than $10,000 worth of agriculture products. Assign that logical vector to the variable agricultureLogical. Apply the which() function like this to identify the rows of the data frame where the logical vector is TRUE. which(agricultureLogical) What are the first 3 values that result?
236, 238, 262
59, 460, 474
125, 238,262
153 ,236, 388



```{r}
if(!file.exists("dataTest")){
dir.create("dataTest")
}

dataOrigin<- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv"  

destfile<-"./dataTest/dataQ1.csv"

if(!file.exists(destfile)){
    getwd()
    download.file(dataOrigin,destfile,method="curl")
}

datos<-read.csv(destfile)

head(datos)

```



De acuerdo con la documentacion  la primera condicion implica que la variable (ACR) tiene que tener un valor de 3 y la variable AGS un valor de 6 


```{r}
agricultureLogical<-((datos$ACR==3)&(datos$AGS==6))
head(agricultureLogical)
which(agricultureLogical)
```


Question 2
--------------------------------------------------------

Using the jpeg package read in the following picture of your instructor into R 

https://d396qusza40orc.cloudfront.net/getdata%2Fjeff.jpg 

Use the parameter native=TRUE. What are the 30th and 80th quantiles of the resulting data? (some Linux systems may produce an answer 638 different for the 30th quantile)
-10904118 -10575416
10904118 -594524
-15259150 -10575416
-15259150 -594524 

empezamos por cargar el package y descargar el archi

```{r}
if(!file.exists("dataTest")){
dir.create("dataTest")
}

dataOrigin<- "https://d396qusza40orc.cloudfront.net/getdata%2Fjeff.jpg" 

destfile<-"./dataTest/dataQ2.jpg"

if(!file.exists(destfile)){
    getwd()
    download.file(dataOrigin,destfile,method="curl")
} 

library(jpeg)
image<-readJPEG(destfile,native=TRUE)
```

ahora que tenemos los datos es tan facil como 

```{r}
quantile(image,probs=c(0.3,0.8))
```


Question 3
--------------


Load the Gross Domestic Product data for the 190 ranked countries in this data set: 

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv 

Load the educational data from this data set: 

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv 

Match the data based on the country shortcode. How many of the IDs match? Sort the data frame in descending order by GDP rank (so United States is last). What is the 13th country in the resulting data frame? 

Original data sources: 
http://data.worldbank.org/data-catalog/GDP-ranking-table 
http://data.worldbank.org/data-catalog/ed-stats
190, Spain
234, Spain
189, St. Kitts and Nevis
189, Spain
190, St. Kitts and Nevis
234, St. Kitts and Nevis


En primer lugar descargamos los archivos y los cargamos en DF


```{r}
if(!file.exists("dataTest")){
dir.create("dataTest")
}

dataOriginGDP<- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv " 

destfileGDP<-"./dataTest/GDP.csv"

if(!file.exists(destfileGDP)){
    getwd()
    download.file(dataOriginGDP,destfileGDP,method="curl")
} 


dataOriginEDU<- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv  " 

destfileEDU<-"./dataTest/EDU.csv"

if(!file.exists(destfileEDU)){
    getwd()
    download.file(dataOriginEDU,destfileEDU,method="curl")
} 

dataGDP<-read.csv(destfileGDP,na.strings=c("","NA"),skip=4,nrows=190)
dataEDU<-read.csv(destfileEDU,na.strings=c("","NA"))
head(dataGDP)
head(dataEDU)
# vamos a retocar un poquito los nombres de dataGDP que asi son feos 
names(dataGDP)[1]<-"ShortCode"
names(dataGDP)[2]<-"GDPRank"
```

Por inspeccion vemos que el codigo de archivo es en dataEdu, "CountryCode", mientras que en GDP es la primera columna que es "ShortCode"  asi que va a tocar hacerlo con merge Ojo, que solo valian los ranked

```{r}
dataMERG<-merge(dataEDU,dataGDP,by.x="CountryCode",by.y="ShortCode")
dim(dataMERG)
```

el numero que coinciden es 189

Para la segunda parte hay que colocarlos por la columna GDPRank, pero antes hay que convertirla en numerica que si no la liamos 

```{r}
dataMERG$GDPRank<-as.numeric(dataMERG$GDPRank)

library(plyr)
dataMERGORD<-arrange(dataMERG,desc(GDPRank))
dataMERGORD[13,2]
```

y por supuesto sale ST kits  

DataMERG nos va a seguir haciendo falta para las proximas 

Question 4
----------------
What is the average GDP ranking for the "High income: OECD" and "High income: nonOECD" group? 

hay que hacerlo por income group 

```{r}
sapply(split(dataMERG$GDPRank,dataMERG$Income.Group),mean)
```


Question 5
---------------

Cut the GDP ranking into 5 separate quantile groups. Make a table versus Income.Group. How many countries are Lower middle income but among the 38 nations with highest GDP?

Metemos los grupos en una nueva variable y hacemos la tabla
```{r}
dataMERG$GDPQ<-cut(dataMERG$GDPRank,5)
table(dataMERG$GDPQ,dataMERG$Income.Group)
```

La respuesta se saca por inspeccion del resultado